% Your second paragraph should be a brief overview of your background as is relevant to the position. Here, you should include key achievements, skills and specialties that make you particularly suited to perform well in the position. Focus on one or two and provide specific details about your success including measurable impacts you made.

% Pay close attention to keywords listed in the job description and include those that you identify with in the body of your cover letter. You should only include information about your most recent one or two professional experiences.

% https://www.indeed.com/career-advice/resumes-cover-letters/how-to-write-a-cover-letter

As the SDE of Mobile Shopping Foundation at Amazon, I am a reliable IC in the organization and am responsible for contributing the Backend of our Mobile App message pushing foundation service, which provides the ability for any feature teams to push their message efficiently to Amazon Shopping App. Before that, I got my Computer Science and Engineering master and bachelor degree from Beihang University and graduated as a top 10\% most excellent student.

When I chose my major before attending the college, I relized that the Computer and Software would be popular and powerful.
Therefore, I had studied for 7 years to get my bachlor and master degree on Computer Science and Engineer. During the college, I finished 5 internships and tried different companies and fileds. Then, I chose to join Amazon with a return offer as a full-stack software engineer. I have been working here for about 1 year and a half. Now, I believe my choice to become a SDE fits me perfectly. I have great passion for programing.
In the future, I plan to transfer my location to Europe for family reason. My girlfriend will study for her CS Master degree in Amsterdam. We are interested in developing our software career further in Europe.